HealpixNet: Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-28 scnn.tex
added TODO at the beginning

\title{Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications}

@@

@@

\subsection{Convolutions on manifolds}

@@

\subsection{Convolutions on point clouds?}

@@

We compare the spherical CNN with a handcrafted feature classifier. \cite{...}
\todo{Tomek: we probably need 1 or two other classifiers.} The features are
constructed using a normalized histogram of the values. We then train a linear
SVN classifier. We tried different kernels, but they were not leading to better
results. For a fair comparison, we increase the amount of training data of the
SVN classifier until the testing error plateau to a fix value.

@@

Show the learned filters and feature maps and try to interpret them.

>>>>

\title{HealpixNet: Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications}

@@

\section{TODO list}
\begin{itemize}
    \item Michael, do you agree with the title HealpixNet
    \item
\end{itemize}

@@

\subsection{Convolutions on manifolds}
\todo{TK and NP: maybe we just describe convolutions on sphere and graph}

@@

\subsection{Convolutions on point clouds?}
\todo{TK and NP: maybe we just describe convolutions on sphere and graph}

@@

We compare the spherical CNN with a handcrafted feature classifier. CITE \cite{...}
\todo{Tomek: we probably need 1 or two other classifiers.} The features are
constructed using a normalized histogram of the values. We then train a linear
SVN classifier. We tried different kernels, but they were not leading to better
results. For a fair comparison, we increase the amount of training data of the
SVN classifier until the testing error plateau to a fix value.

@@

Show the learned filters and feature maps and try to interpret them.
\todo{\\ TK and NP: Figure of filters from the mass map clasification}
